\section{Model 1 - Saas-Mode}
\begin{enumerate}
	\item The building blocks we see are the firewalls (conceptual).
	The purpose of these firewalls are obviously security related, such that the site is protected from malicious attacks.
	We also see load balancers and filtering.
	These are for work distribution and are also conceptual.
	The other components are all physical, namely the servers (application and database), databases and NAS devices.
	These are for storing and sharing the information on the site.
	
	\item You see the red lines connecting components within a site to each other.
	This represent how components in a site are linked to each other and with which components they can communicate.
	You also see the green arrows, these connectors show how the main site communicates with the secondary site(s).
	All these connectors are conceptual.
	
	\item 
    \begin{description}
        \item[Logical view] We see a clear logical view with regards to the communication.
	    You can clearly see which components should interact with other components.
        Since the model is comprised of a network overview, network operators benefit from this model.
        \item[Physical view] You can clearly see all the components in the view and it gives an overview of the services.
        This is particularly useful to a system engineer.
    \end{description}
	
	\item
	\begin{description}
		\item[Performance/Scalability] Yes, the use of the filtering and clustering give notion of the performance of the model.
		Also the scalable parts are shown in groups from 1, 2 to N.
		\item[Availability/Reliability] No.
		\item[Security] Yes, the use of firewalls and synchronous replications define the security.
		\item[Maintainability] No.
	\end{description}
	
	\item Yes, You can clearly see the flow throughout the system.
	You see load balancers, applications, filters, Clustered Databases, Severs and NAS devices and how these are linked to each other.
	
	\item You can clearly see what all the components in the sites are and how they are connected.
	Different components have there own colouring and smaller parts of the model, belonging to each other are structured in a group (dashed lines).
	Different ways of communication are shown with different arrows.
	Not really clear what the model does precisely and what users/systems are using it.
\end{enumerate} 